\texttt{Taxonomic supertree construction with}\texttt{\emph{ Incertae sedis}}\texttt{ taxa}

### 2018-05-09 doc/incertae_sedis.tex
blah

However, this assumes that \emph{incertae sedis} taxa are always
placed within their siblings, or descendants of their siblings.
As
such, it does not handle cases such as Figure \ref{fig:Placing-one-incertae}, 
in which $I$ is first placed as sibling to $AI$, and then
$AI$ is placed within $I$.
Note that $I$ is not a sibling of $AI$ or a
descendant of a sibling.
Furthermore, the MRCA of $I$ and $AI$ is the
root, and the path from $AI$ to the root includes $A$, but $A$ is not
broken.
We suggest that this conundrum may be resolved by first
processing the placement of $I$ within $A$ by modifying the taxonomy
to reflect this placement\footnote{Does this actually work? Some
placements break taxa.}.
When we consider the placement of $AI$ within
$I$ on this modified taxonomy, the MRCA of $I$ and $AI$ is now $A$
instead of the root, and the correct interpretation results.
We
suggest that by walking the tree in a pre-order fashion and processing
shallowing placements first, the previous approach of finding the MRCA
and labelling intermediate nodes as either additional placements or
broken incertae sedis (or incertae\_sedis\_inherited) taxa holds.
Such
an approach should also handle cases containing nested incertae sedis
taxa, as in Figure \ref{fig:Placing-one-incertae}.

>>>>

% However, this assumes that \emph{incertae sedis} taxa are always
% placed within their siblings, or descendants of their siblings.
% As
% such, it does not handle cases such as Figure \ref{fig:Placing-one-incertae}, 
% in which $I$ is first placed as sibling to $AI$, and then
% $AI$ is placed within $I$.
% Note that $I$ is not a sibling of $AI$ or a
% descendant of a sibling.
% Furthermore, the MRCA of $I$ and $AI$ is the
% root, and the path from $AI$ to the root includes $A$, but $A$ is not
% broken.
% We suggest that this conundrum may be resolved by first
% processing the placement of $I$ within $A$ by modifying the taxonomy
% to reflect this placement\footnote{Does this actually work? Some
% placements break taxa.}.
% When we consider the placement of $AI$ within
% $I$ on this modified taxonomy, the MRCA of $I$ and $AI$ is now $A$
% instead of the root, and the correct interpretation results.
% We
% suggest that by walking the tree in a pre-order fashion and processing
% shallowing placements first, the previous approach of finding the MRCA
% and labelling intermediate nodes as either additional placements or
% broken incertae sedis (or incertae\_sedis\_inherited) taxa holds.
% Such
% an approach should also handle cases containing nested incertae sedis
% taxa, as in Figure \ref{fig:Placing-one-incertae}.
